---
title: "CRUF"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(mice)
library(xtable)

```


<!-- badges: start -->
[![Travis build status](https://travis-ci.org/Ygall/CRUF.svg?branch=master)](https://travis-ci.org/Ygall/CRUF)
<!-- badges: end -->

Clinical Research Utilities Functions (CRUF) : Useful functions for clinical research data analysis.

## Functions

- tabkris_2 : Description table with options
- Survival :
  - Univariate : Compute and format multiple univariate cox model in a single table
  <!-- - Multivariate : Format a multivariate cox model in a single table -->
- Logistic regression :
  - Univariate : Compute and format multiple univariate logistic model in a single table
  - Multivariate : Format a multivariate logistic model in a single table
- Logistic regression with cluster :
  - Univariate : Compute and format multiple univariate logistic model in a single table, using robust sandwich variance estimation
  - Multivariate : Format a multivariate logistic model in a single table, using robust sandwich variance estimation
- Others :
  - Format p-value with stars such as R does in summary of models
  - Coerce factor to numeric with actual values

## Installation

Released version is available on [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("CRUF")
```

Development version is available on [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Ygall/CRUF")
```
# Manual

```{r child = 'vignettes/manual.Rmd'}
```
